---
title: "p8105_hw1_zh2596"
author: "Zilin Huang"
date: "`r Sys.Date()`"
output: github_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(moderndive)
library(ggplot2)
library(tidyverse)
```

# Problem 1

Load the dataset:

```{r 1}
data("early_january_weather")
```

This dataset includes `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 

Its variables include `origin` with character value "EWR"; `year, month, day, hour` with the recording time, `temp, dewp, humid` with the recorded float data type of temperature, dewpoint, and humidity; `wind_dir, wind_speed, wind_gust` with the recorded floating value of wind direction, speed, and gust speed (which contains much missing values); `precip` with almost all of its numeric values of precipitation as 0; `pressure` with most of the value of sea level pressure close to 1000 or missing; `visib` with the recorded floating value of visibility; `time_hour` with the date value corresponding to the columns of `year, month, day, hour`.

The mean temperature is `r mean(early_january_weather$temp)`.

The scatterplot of temperature against the date is shown here:

```{r 2, message=FALSE}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color= humid)) + geom_point()
```

It seems like the temperature fluctuates with an tendency of increase (approximately from 25F to 50F) as time passes, and the humidity level increases as well. The scatterplot behaves like a line chart in a discrete form.

This scatterplot is exported to the directory as a pdf document, named as "p8105_hw1_scatterplot":

```{r 3, message=FALSE}
ggsave("p8105_hw1_scatterplot.pdf")
```

# Problem 2

Create a data frame named "p8105_hw1_df":

```{r 4}
p8105_hw1_df <- tibble(rand_vec = rnorm(10),
                       logical_vec = rand_vec > 0,
                       char_vec = c("1mean(pull(p8105_hw1_df, var=2))","2","3","4","5","6","7","8","9","10"),
                       fac_vec = factor(c(1,1,1,2,2,2,2,3,3,3)))
```

Using the `pull` function to try take the mean of each variable in the dataframe:

```{r 5}
# Mean of the random sample:
mean(pull(p8105_hw1_df, var=1))
# Mean of the logical vector:
mean(pull(p8105_hw1_df, var=2))
# This generates an error:
# mean(pull(p8105_hw1_df, var=3))
# This generates an error:
# mean(pull(p8105_hw1_df, var=4))
```

Using the `as_numeric` functions to convert the logical, character, and factor variables to numeric values:

```{r 6, eval=FALSE}
as.numeric(pull(p8105_hw1_df, var=2))
as.numeric(pull(p8105_hw1_df, var=3))
as.numeric(pull(p8105_hw1_df, var=4))
```

For the logical vector, since by default, `TRUE` is 1 and `FALSE` is 0, I can take the mean of this vector directly, without the necessity of transforming it to numeric values. 

After the numeric transformation, I can take the mean of the character vector, which is `r mean(as.numeric(pull(p8105_hw1_df, var=3)))`. This is because inside the character values themselves are not considered as numeric values for computation, even if they contain numbers (like "1", "2", etc.)

Also, I can take the mean of the factor vector, which is `r mean(as.numeric(pull(p8105_hw1_df, var=4)))`. This is because inside the original factor vector, the factor level itself cannot be specified as numeric values in order to conduct calculations.  